\hypertarget{table-of-contents}{%
\section{Table Of Contents}\label{table-of-contents}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \protect\hyperlink{introduction}{Introduction}

  \begin{enumerate}
  \def\labelenumii{\arabic{enumii}.}
  \tightlist
  \item
    \protect\hyperlink{ux5cux23introduction}{Introduction}
  \item
    \protect\hyperlink{problem-statement}{Problem Statement}
  \item
    {[}{[}\#Objectives{]}{]}
  \item
    {[}{[}\#Scope{]}{]}
  \end{enumerate}
\item
  {[}{[}\#Literature Survey{]}{]}

  \begin{enumerate}
  \def\labelenumii{\arabic{enumii}.}
  \tightlist
  \item
    {[}{[}\#Literature/Techniques studied{]}{]}
  \item
    {[}{[}\#Paper/Findings{]}{]}
  \end{enumerate}
\item
  {[}{[}\#Analysis and Design{]}{]}

  \begin{enumerate}
  \def\labelenumii{\arabic{enumii}.}
  \tightlist
  \item
    {[}{[}\#Analysis of the system{]}{]}
  \item
    {[}{[}\#Proposed Solution{]}{]}
  \item
    {[}{[}\#Design of the proposed system{]}{]}
  \end{enumerate}
\item
  {[}{[}\#Results and Discussion{]}{]}
\item
  {[}{[}\#Conclusion and Future Work{]}{]} {[}{[}\#References{]}{]} \#
  Introduction \#\# Introduction \#\# Problem Statement Every year
  forest fires destroy a huge area of forest cover, leaving large-scale
  destruction of flora and fauna in it's wake. Forest fires play a major
  role in driving thousands of species of wildlife to extinction every
  year. Artificial intelligence helps us predict the future and using it
  in this domain can successfully help us predict forest fires and save
  the wildlife. \#\# Objectives
\end{enumerate}

\begin{itemize}
\tightlist
\item
  Provide real-time visual reference of forest fire probability around
  the world.
\item
  Minimize damage and if possibly prevent it.
\item
  Providing early contingency warning for upcoming wildfires. \#\# Scope
  \#\#\# 2019-2020 Australian Bushfires
\item
  Australia was hit hard by bushfires during summer 2019-20 - the most
  catastrophic bushfire season ever experienced in the country's
  history. So much was lost, and the impacts will be felt for years to
  come.
\item
  Early in January 2020, WWF estimated that at that time, 1.25 billion
  animals had been killed. As the fires raged well into March, and
  destroyed even more habitat, we had a scientific duty to update that
  figure to understand the true impact on our wildlife and natural
  landscapes.
\item
  Up to 19 million hectares were burnt, with 12.6 million hectares
  primarily forest and bushland. 33 lives were lost and around 3,094
  homes destroyed. \#\#\# Using an AI model to provide real-time updates
  on the
\end{itemize}

\hypertarget{literature-survey}{%
\section{Literature Survey}\label{literature-survey}}

\hypertarget{literaturetechniques-studied}{%
\subsection{Literature/Techniques
studied}\label{literaturetechniques-studied}}

\hypertarget{papersfindings}{%
\subsection{Papers/Findings}\label{papersfindings}}

\hypertarget{analysis-and-design}{%
\section{Analysis and Design}\label{analysis-and-design}}

\hypertarget{analysis-of-the-system}{%
\subsection{Analysis of the system}\label{analysis-of-the-system}}

\hypertarget{propsed-solution}{%
\subsection{Propsed Solution}\label{propsed-solution}}

\hypertarget{design-of-the-proposed-system}{%
\subsection{Design of the proposed
system}\label{design-of-the-proposed-system}}

\hypertarget{results-and-discussion}{%
\section{Results and Discussion}\label{results-and-discussion}}

\hypertarget{conclusion-and-future-work}{%
\section{Conclusion and Future Work}\label{conclusion-and-future-work}}

\hypertarget{references}{%
\section{References}\label{references}}
